### 2014-10-08 D1-3.tex
Partial cleanup up formatting and arrangement of sections.
Added authors. Upated TOC.  Cleanup Formatting mainly.

@@

\setcounter{tocdepth}{1}

@@

\section{Implementation}
\subsection{Authentification and Access Control}
\subsection{Anonymization and Pseudonoymization}
\subsection{Randomization}

\chapter{Improved Sensor Data Mining Methods}
\section{Battery Awareness of Sensor Collector}
Results from Projektprakikum (Wifi/Zip)

\section{Service Line Detection (new method)}
MA thesis results from Sven Milker

\section{Issue Analysis}
Christoph Schäfer with Niko Beck

\bibliography{D1-3}

\end{document}

>>>>

\LGaddauthorNoPhone{UKob}{Maximilan Meffert}%
{}

\LGaddauthorNoPhone{BIZ}{Maite de Arana Agiretxe}%
{\small komunikazioa.tekniko1@biscaytik.eu}

@@

\setcounter{tocdepth}{2}

@@

\chapter{Implementation of Privacy Protection Measures}
\subsection{Privacy Policy}
\subsection{Privacy Dashboard}
\subsection{Transfer Encryption (HTTPS/SSL)}
\subsection{Database Access Policies}
\subsection{Anonymization of recorded trips}
\subsection{Randomization of GPS data}

\bibliography{D1-3}
\end{document}

### 2014-10-08 PrivacyProtection-2014-09-09.tex
Added authors. Upated TOC.  Cleanup Formatting mainly.

\chapter{Legal and Ethical aspects of Privacy}
\label{chap:privacy}

@@

The term informational privacy as conceptual foundation of privacy originates from the juristic discussion The Right to Privacy (1890) by Warren and Brandeis.
The arise of new technologies like photography combined with a growing press created an increased publicity.
Warren and Brandeis were worried that existing law like castle doctrines or libel and slander could not suffice.
They felt a need for a new right to "protect the extent to wich one's thoughts, sentiments, and emotions could be shared with others" [1].
This right would be "the right to be left alone".

The right to "protect the extent to wich one's thoughts, sentiments, and emotions could be shared with others" by Warren and Brandeis was later extend to cover arbitrary information and is now kown as the privacy concept "... the control we have over information about ourselves ..." [2].

@@

``(1) Everyone has the right to respect for his private and family life, his home and his correspondence. (2) There shall be no interference by a public authority with the exercise of this right except such as is in accordance with the law and is necessary in a democratic society in the interests of national security, public safety or the economic well-being of the country, for the prevention of disorder or crime, for the protection of health or morals, or for the protection of the rights and freedoms of others.'' {[}\hyperref[references]{3}{]}

``The European Court of Human has given this article a very broad
interpretation in its juresprudence.'' {[}\hyperref[references]{2}{]}

@@

``The directive regulates the processing of personal data regardless of whether such processing is automated or not.''
{[}\hyperref[references]{1}{]} where:

\begin{itemize}
\item
  \textbf{personal data} is ``any information relating to an identified or identifiable natural person {[}\ldots{}{]} (art. 2a)''
  {[}\hyperref[references]{1}{]}
\item
  \textbf{processing} is ``any operation or set of operations which is performed upon personal data {[}\ldots{}{]} (art. 2b)''
  {[}\hyperref[references]{1}{]}
\end{itemize}

The ``identified or identifiable natural person'' is called \textbf{data subject}.

The sole responsibility for compliance is held by so called \textbf{controllers}.
A controller is an actor ``which alone or jointly with others dertimines the purposes and means of the processing of personal data; (art 2d)''
{[}\hyperref[references]{1}{]}

This rule is applicable ``whenever the controller uses equipment situated within the EU''{[}\hyperref[references]{1}{]}.
This will hold for every e-commerce provider \textbf{inside or outside} of the EU because the customer's computer is \emph{situated within the EU} anyways.

``Personal data should not be processed at all, except when certain conditions are met'' {[}\hyperref[references]{1}{]}.
These conditions incorporate the seven OECD princepals and are futher categorized in the categories:

\begin{itemize}
\item
\textbf{Transparency}: ``The data subject has the right to be informed when his personal data is being processed {[}\ldots{}{]} (art. 10 and 11)'' {[}\hyperref[references]{1}{]} and he has the right how and by whom it is processed.
Additionally other speficied requirements have to be met, i.e.~giving consent.
\item
\textbf{Legitimate prupose}: ``Personal data can only be processed for specified explicit and legitimate pruposes and may not be processes futher in a way incompatible with those pruposes (art. 6b)''
{[}\hyperref[references]{1}{]}.
\item
\textbf{Proportionality}: ``Personal data may be processed only insofar as it is adequate {[}\ldots{}{]} in relation to {[}its{]} pruposes {[}\ldots{}{]}; every reasonable step must be taken to ensure that data wich are inaccurate or incomplete {[}\ldots{}{]} are erased or rectified (art. 6)'' {[}\hyperref[references]{1}{]}
\end{itemize}

@@

Member states have to create independent \textbf{supervisory authorities} for personal data processing where controllers have to register before they start to process any data.
The record has to be stored in public register {[}\hyperref[references]{1}{]}.

@@

all between the US and the EU, although the US has no comparable law of data protection. 
The US Supreme Court regards privacy as \textbf{implicit} right granted with the First Amendment. However, european law states privacy as \textbf{explicit} right (ECHR Art. 8).
Additionally the US government follows a doctrine which favors the economy to implement self-regulation {[}\hyperref[references]{1}{]}.

@@

Germany implements Directive 95/46 with the \emph{Federal Data Protection Act} from 2001 known as \emph{Bundesdatenschutzgesetz (BDSG)} {[}\hyperref[references]{1}{]}{[}\hyperref[references]{2}{]}{[}\hyperref[references]{6}{]}.
However, Germany has violated the directive in two points:

\begin{enumerate}
\item
The BDSG has become effective three years too late, thus the EC filed a treaty violation proceeding against Germany {[}\hyperref[references]{6}{]}.

\item
The BDSG does not implement \textbf{independet} supervisory authorities. 
The \emph{Bundesdatenschutzbeauftragter} is subordinate to the Ministiry of Interior. 
Although he is not subject to technical oversight (\emph{Fachaufsicht}), he is subject to staff supervision by the government (\emph{Rechtsaufsicht} durch die Bundesregierung und  \emph{Dienstaufsicht} durch das Innenministerium) and budget oversight (including approval of employees) by the ministry {[}\hyperref[references]{7}{]}. 
Thus the EC filed a treaty violation proceeding against Germany, again {[}\hyperref[references]{6}{]}. 
In March 2010 Germany was found guilty of violation of Directive 95/46 by the ECJ {[}\hyperref[references]{6}{]}.
\end{enumerate}

@@

The states of Germany have their own implementation of Directive 95/46 (\emph{Landesdatenschutzgesetze}).
Federal public authorites are only bound to their federal law. {[}\hyperref[references]{2}{]}

Churches are not subject the BDSG. {[}\hyperref[references]{2}{]}

@@

The UK implements Directive 95/46 with the \emph{Data Protection Act 1998 (DPA)} {[}\hyperref[references]{1}{]}{[}\hyperref[references]{3}{]}.

The act is knwon for its high complexity: a manual record of phone numbers for business purposes could be hold subject to the DPA {[}\hyperref[references]{3}{]}.
Although the act seems to fully cover the directive.
Even higher restriction apply for \emph{``sensitive personal data''} (race, ethnicity, politics, religion, trade union status, health, sex life or criminal record), i.e. \textbf{consent} must be given freely and has to be explicit. {[}\hyperref[references]{3}{]}

@@

\item
Require that their data is not used for direct marketing. {[}\hyperref[references]{3}{]}
\end{itemize}

@@

France implements Directive 95/46 with Law 2004-801 modifying law 78-17 of 6.1.1978 (\emph{Loi n° 2004-801 du 6 août 2004} modifying \emph{loi n°78-17 relative à l'informatique, aux fichiers et aux libertés}) {[}\hyperref[references]{1}{]}{[}\hyperref[references]{10}{]}{[}\hyperref[references]{11}{]}.

@@

The USA do not implement the directive, nor is there any obligation for them to do so.
However, companies subject to US jurisdiction can be certified to comply with the seven principles enforced by Directive 95/46 (the seven OECD recommendations) {[}\hyperref[references]{5}{]}.
Thus, those companies will act as \emph{safe harbors}. Without certification foreign companies are not allowed to send customer data back home {[}\hyperref[references]{9}{]}.

\emph{Safe harbor} in general is the legal concept to regulate that a certain conduct will be deemed {[}\hyperref[references]{4}{]}, but in germany the term is commonly used as synonym for the agreement between the EU and the US regarding Directive 95/46.)

@@

Defining privacy is a challenge which seems impossible. This is well put to words by Serge Gutwirth, who notes: \emph{``The notion of privacy remains out of the grasp of every academic chasing it. Even when it is cornered by such additional modifiers as `our' privacy, it still finds a way to remain elusive.''} {[}\hyperref[references]{2}{]}.

Many privacy researchers seem to ``forcus on the ways in which privacy can be infrenged'' {[}\hyperref[references]{1}{]}.
Thus they try to create taxonomies of \emph{privacy harms} instead of taxonomies of \emph{privacy types}.
Those two differ in the respect that the former focuses on threats to prohibit whereas the latter focuses on values to protect.
So one should rather evaluate what aspects are precious about privacy and develop measures to ensure their security than only forbid single actions against privacy {[}\hyperref[references]{1}{]}.

@@

This type is the right keep body functions and body characteristics
private {[}\hyperref[references]{1}{]}. It maps the one by Clarke.

@@

This type is also concerned with the ``protection against disclosure of personal matters'' {[}\hyperref[references]{1}{]} through behaviour, however Clarke's distinction between ``casual observation {[}\ldots{}{]} systematic recording and storage of information about those activities'' {[}\hyperref[references]{1}{]}is lifted.

@@

It ``aims to avoid the interception of communications'' {[}\hyperref[references]{1}{]} either electronic or face-to-face.

Examples include:
\begin{itemize}
\item Secrecy of letters ('Briefgeheimnis' in german Legislation).
\item Email contents
\item Personal direct communication
\item Right to free discussion, i.e.~without third parties listening
\end{itemize}

@@

This type is concerned with ``making sure that individuals's data is not
automatically available to other individuals and organisations''
{[}\hyperref[references]{1}{]}. This is Informational Privacy in an
intuitive sense.

@@

This type is the right ``not to share their thoughts or feelings or to
have those thoughts or feeling (sic!) revealed''
{[}\hyperref[references]{1}{]}. It is concerned with (automatic) emotion
detection. This type is the counterpart the \emph{Privacy of the Person}
like body and mind are counterparts of one another (dualism).

@@

This type is the right ``to move about in public or semi-public space
withoug being identified, tracked or monitored'' {[}\hyperref[references]{1}{]}.
Additionally this type is concerned with the protection of one's home and private places (``right to solitude'' {[}\hyperref[references]{1}{]}).

@@

This type is the right ``to associate with whomever {[}one{]} wish, withoug being monitored'' {[}\hyperref[references]{1}{]}.
It is concerned with the protection against the automatic record of one's contacts.
It does not imply that one is monitored because of the associations.

@@

\item
  \textbf{Privacy of The Person:} reflexive violation
\item
  \textbf{Privacy of Behaviour and Action:} none
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Some psychological diseases
  (e.g.~depression) have physiological impact. Such physiological
  patterns could be detected.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} none
\end{itemize}

\paragraph*{Privacy of Behaviour and Action}

The Privacy of Behaviour and Action is concerned with one's privacy
regarding social activities (religious, political, sexual, \ldots{}). If
this type is violated, following implicit violations are possible:

\item
  \textbf{Privacy of The Person:} Religious practices may include body
  modifications (e.g.~circumcision).
\item
  \textbf{Privacy of Behaviour and Action:} reflexive violation
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Social activities in
  general depend on a certain intellectual attitude. Such an actvity is
  the expressions of such an attitude.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} Recording religious, politcal or
  sexual activities can reveal association with churches, political
  parties or sexual partners.
\end{itemize}

@@

The \textbf{Privacy of The Person} is generally concerned with one could
best understand as \emph{Biometric Privacy}. Friedewald et al. paraphase
it as \emph{``{[}\ldots{}{]} the right to keep body functions and body
characteristics {[}\ldots{}{]} private''}. \textbf{Accelerometer},
\textbf{Rotation Vector} and \textbf{Gyroscope} measure the physical
movement of the mobile device on all three axes. If the moblile device
is carried \emph{``normally''} its safe to say that those sensors also
measure the movments of its carrier. So his privacy is infringed
regarding biometric behaviour, as it is captured automatically.
(\textbf{Note:} This is not to be confused with the \textbf{Privacy of
Behaviour and Action} which is used for the social aspects of behaviour
action, e.g.~praying, sexual habits or poltical activities.)

@@

The \textbf{Privacy of Association} sates that everyone has the
\emph{``right to associate with whomever they whish, without being
monitored {[}automatically without reasonable suspicion{]}''}. This
includes indivisuals and organizations. \textbf{WLAN} and
\textbf{Bluetooth} sensors provide the ability to monitor such
associations if their lists contain kown entities. If one frequently
connects with an organizational wirelss network, e.g.~an university
network, an association can be deduced (student or staff). The same goes
for the \textbf{Bluetooth} sensor, if it is stationary. Additionally, if
the recorded bluetooth clients are mobile, it is more or less possible
to deduce association with the technical identity of (yet) anonymous
individuals.

@@

\subparagraph{1 Privacy of the Person}

\emph{``This type is the right keep body functions and body
characteristics private''} {[}\hyperref[references]{1}{]}. Here we are
concerned with the personal physiological and psychological privacy of
citizens. This privacy is threatened if \textbf{body characteristics}
(weight, height, body measures, fingerprints, dna,\ldots{}) or
\textbf{medical conditions} (limping, having a cold, suffering from
depression, visiting therapists or other doctors) \textbf{can be
revealed or inferred}.

The Live+Gov project collects sensor data from mobile devices
(accellerometer, location, \ldots{}). By applying \emph{human activity
recognition (HAR)} techniques we could detect certain movement patterns
and in fact detect limping or other pathologic movements. Additionally
we know the position with of indiviual citizens with a sufficient
accurancy, and the Live+Gov project is only applied to a destinct urban
area. So we could link HAR data with the yellow pages, filter for
medical specialists and limit the possibilities of pathologic
conditions. But even without HAR data we could determine a likelihood
for certain conplaints. Frequent vistits to the dentist does not imply
healthy teeth.

@@

\emph{``This type is also concerned with the `protection against
disclosure of personal matters' through behaviour''}
{[}\hyperref[references]{1}{]}. This type is concered with religous
practices, sexaul habits, political activities, etc. revealed through
observation. For the Live+Gove project this type is related to the
Privacy of Location and Space and the Privacy of Association. Locational
data is recorded by default and by linking it to maps and public
registers like phone books those *``personal matters*" could be
disclosed by frequently visited places (churches, brothels, party head
quaters, \ldots{}).

\subparagraph{3 Privacy of Communication}

\emph{``It `aims to avoid the interception of communications' either
electronic or face-to-face''} {[}\hyperref[references]{1}{]}. This type
is threatened if we intrude the secrecy of correspondence, posts and
telecommunications, personal direct communication or right to free
discussion without third parties listening. The Live+Giv project only
could threaten this type by using mobile client application as trojan
horse, collecting any communication data (chat, sms, microphone).

@@

\emph{``This type is concerned with `making sure that individuals's data
is not automatically available to other individuals and
organisations'\,''} {[}\hyperref[references]{1}{]}. This is
Informational Privacy in an intuitive sense regarding data like:

@@

\emph{``This type is the right `not to share their thoughts or feelings
or to have those thoughts or feeling (sic!) revealed'\,''}
{[}\hyperref[references]{1}{]}. This means thoughts and emotions must
not be detected autmatically. Intuitively the Live+Gov system seems
unable to threaten this type. However, considering the issue component
of the Urban Maintaince use case, this might reveal information about
one's thoughts regarding the community in a positive manner. Solely by
taking part we could assume a caring personality. This threatens one's
privacy in a rather technical sense, but does not necessarily impose any
harm.

@@

\emph{``This type is the right `to move about in public or semi-public
space withoug being identified, tracked or monitored'. Additionally this
type is concerned with the protection of one's home and private places
(`right to solitude')''} {[}\hyperref[references]{1}{]}. The location
dimension of this type is relatively easy to understand: The
geo-position of citizens cannot be monitored by default. However, by
actively taking part in the Live+Gov project, the locational privacy of
citizens is threatened by default because data of the location sensor
will be collected. The space dimension is more complex, but can be
simplified with a \emph{``right to solitude''}. This dimension could be
threatend with the invasion of personal space in any means, i.e.~by
disrespecting one's right to an inviolate home or by undercutting one's
comfort zone in an conversation. Live+Gov only utilizes the mobile
devices of citizens, so we could disrespect the former by activating the
phone's micropone and start recording.

@@

\emph{``This type is the right `to associate with whomever {[}one{]}
wish, withoug being monitored'.''} {[}\hyperref[references]{1}{]}. This
means that one's associations must not be recoreded by default
independet from any suspicion. Anyhow, it does not mean that this right
cannot be forfeit given a reasonable suspicion. The Live+Gov project
could easily threaten this type just by linking locational data with
yellow pages and a map. Even if an association graph cannot be deducted
for individual citizens, we could aggregate the data to create an
association graph for a whole population as the Live+Gov system is
applied to a restricted urban area.

@@

This is a note on an excerpt from the article \emph{Sociotechnical
Architecture for Online Privacy} {[}\hyperref[references]{1}{]} called
\textbf{The 7 C's of user privacy control}. Those 7 C's are aspects
which should be covered by measures for implementing user privacy. They
derive from an interpretation of privacy which could be summarized as
\emph{``One's ability to control/seclude information about themselve''}.

>>>>

>\chapter{Legal and Ethical aspects of Privacy}
\label{chap:privacy}

@@

The term informational privacy as conceptual foundation of privacy originates from the juristic discussion The Right to Privacy (1890) by Warren and Brandeis.
The arise of new technologies like photography combined with a growing press created an increased publicity.
Warren and Brandeis were worried that existing law like castle doctrines or libel and slander could not suffice.
They felt a need for a new right to "protect the extent to wich one's thoughts, sentiments, and emotions could be shared with others" \cite{1}.
This right would be "the right to be left alone".

The right to "protect the extent to wich one's thoughts, sentiments, and emotions could be shared with others" by Warren and Brandeis was later extend to cover arbitrary information and is now kown as the privacy concept "... the control we have over information about ourselves ..." \cite{2}.

@@

``(1) Everyone has the right to respect for his private and family life, his home and his correspondence. (2) There shall be no interference by a public authority with the exercise of this right except such as is in accordance with the law and is necessary in a democratic society in the interests of national security, public safety or the economic well-being of the country, for the prevention of disorder or crime, for the protection of health or morals, or for the protection of the rights and freedoms of others.'' \cite{2}

``The European Court of Human has given this article a very broad
interpretation in its juresprudence.'' \cite{2}

@@

``The directive regulates the processing of personal data regardless of whether such processing is automated or not.'' \cite{1} where \emph{personal data} is ``any information relating to an identified or identifiable natural person [...] (art. 2a)'' and \emph{processing} is ``any operation or set of operations which is performed upon personal data [...] (art. 2b)'' \cite{1}

The ``identified or identifiable natural person'' is called \emph{data subject}.

The sole responsibility for compliance is held by so called \textbf{controllers}.
A controller is an actor ``which alone or jointly with others dertimines the purposes and means of the processing of personal data; (art 2d)''
\cite{1}

This rule is applicable ``whenever the controller uses equipment situated within the EU''\cite{1}.
This will hold for every e-commerce provider \textbf{inside or outside} of the EU because the customer's computer is \emph{situated within the EU} anyways.

``Personal data should not be processed at all, except when certain conditions are met'' \cite{1}.
These conditions incorporate the seven OECD princepals and are futher categorized in the categories:

\begin{itemize}
\item
\textbf{Transparency}: ``The data subject has the right to be informed when his personal data is being processed [...] (art. 10 and 11)'' \cite{1} and he has the right how and by whom it is processed.
Additionally other speficied requirements have to be met, i.e.~giving consent.
\item
\textbf{Legitimate prupose}: ``Personal data can only be processed for specified explicit and legitimate pruposes and may not be processes futher in a way incompatible with those pruposes (art. 6b)''
\cite{1}.
\item
\textbf{Proportionality}: ``Personal data may be processed only insofar as it is adequate [...] in relation to [its] pruposes [...]; every reasonable step must be taken to ensure that data wich are inaccurate or incomplete [...] are erased or rectified (art. 6)'' \cite{1}
\end{itemize}

@@

Member states have to create independent \textbf{supervisory authorities} for personal data processing where controllers have to register before they start to process any data.
The record has to be stored in public register \cite{1}.

@@

all between the US and the EU, although the US has no comparable law of data protection. 
The US Supreme Court regards privacy as \textbf{implicit} right granted with the First Amendment. However, european law states privacy as \textbf{explicit} right (ECHR Art. 8).
Additionally the US government follows a doctrine which favors the economy to implement self-regulation \cite{1}.

@@

Germany implements Directive 95/46 with the \emph{Federal Data Protection Act} from 2001 known as \emph{Bundesdatenschutzgesetz (BDSG)} \cite{1}\cite{2}\cite{6}.
However, Germany has violated the directive in two points:

\begin{enumerate}
\item
The BDSG has become effective three years too late, thus the EC filed a treaty violation proceeding against Germany \cite{6}.

\item
The BDSG does not implement \textbf{independet} supervisory authorities. 
The \emph{Bundesdatenschutzbeauftragter} is subordinate to the Ministiry of Interior. 
Although he is not subject to technical oversight (\emph{Fachaufsicht}), he is subject to staff supervision by the government (\emph{Rechtsaufsicht} durch die Bundesregierung und  \emph{Dienstaufsicht} durch das Innenministerium) and budget oversight (including approval of employees) by the ministry \cite{7}. 
Thus the EC filed a treaty violation proceeding against Germany, again \cite{6}. 
In March 2010 Germany was found guilty of violation of Directive 95/46 by the ECJ \cite{6}.
\end{enumerate}

@@

The states of Germany have their own implementation of Directive 95/46 (\emph{Landesdatenschutzgesetze}).
Federal public authorites are only bound to their federal law. \cite{2}

Churches are not subject the BDSG. \cite{2}

@@

The UK implements Directive 95/46 with the \emph{Data Protection Act 1998 (DPA)} \cite{1}\cite{3}.

The act is knwon for its high complexity: a manual record of phone numbers for business purposes could be hold subject to the DPA \cite{3}.
Although the act seems to fully cover the directive.
Even higher restriction apply for \emph{``sensitive personal data''} (race, ethnicity, politics, religion, trade union status, health, sex life or criminal record), i.e. \textbf{consent} must be given freely and has to be explicit. \cite{3}

@@

\item
Require that their data is not used for direct marketing. \cite{3}
\end{itemize}

@@

France implements Directive 95/46 with Law 2004-801 modifying law 78-17 of 6.1.1978 (\emph{Loi n° 2004-801 du 6 août 2004} modifying \emph{loi n°78-17 relative à l'informatique, aux fichiers et aux libertés}) \cite{1}\cite{10}\cite{11}.

@@

The USA do not implement the directive, nor is there any obligation for them to do so.
However, companies subject to US jurisdiction can be certified to comply with the seven principles enforced by Directive 95/46 (the seven OECD recommendations) \cite{5}.
Thus, those companies will act as \emph{safe harbors}. Without certification foreign companies are not allowed to send customer data back home \cite{9}.

\emph{Safe harbor} in general is the legal concept to regulate that a certain conduct will be deemed \cite{4}, but in germany the term is commonly used as synonym for the agreement between the EU and the US regarding Directive 95/46.)

@@

Defining privacy is a challenge which seems impossible. This is well put to words by Serge Gutwirth, who notes: \emph{``The notion of privacy remains out of the grasp of every academic chasing it. Even when it is cornered by such additional modifiers as `our' privacy, it still finds a way to remain elusive.''} \cite{2}.

Many privacy researchers seem to ``forcus on the ways in which privacy can be infrenged'' \cite{1}.
Thus they try to create taxonomies of \emph{privacy harms} instead of taxonomies of \emph{privacy types}.
Those two differ in the respect that the former focuses on threats to prohibit whereas the latter focuses on values to protect.
So one should rather evaluate what aspects are precious about privacy and develop measures to ensure their security than only forbid single actions against privacy \cite{1}.

@@

This type is the right keep body functions and body characteristics private. It maps the one by Clarke.

@@

This type is also concerned with the ``protection against disclosure of personal matters'' through behaviour, however Clarke's distinction between ``casual observation [...] systematic recording and storage of information about those activities'' is lifted.

@@

It ``aims to avoid the interception of communications'' either electronic or face-to-face.

Examples include:
\begin{itemize}
\item Contents of letters and emails
\item Personal direct communication
\item Right to free discussion, i.e.~without third parties listening
\end{itemize}

@@

This type is concerned with ``making sure that individuals's data is not automatically available to other individuals and organisations''. This is Informational Privacy in an intuitive sense.

@@

This type is the right ``not to share their thoughts or feelings or to have those thoughts or feeling (sic!) revealed''.
It is concerned with (automatic) emotion detection.
This type is the counterpart the Privacy of the Person like body and mind are counterparts of one another (dualism).

@@

This type is the right ``to move about in public or semi-public space withoug being identified, tracked or monitored''.
Additionally this type is concerned with the protection of one's home and private places (``right to solitude''.

@@

This type is the right ``to associate with whomever [one] wishes, withoug being monitored''.
It is concerned with the protection against the automatic record of one's contacts.
It does not imply that one is monitored because of the associations.

@@

\item
  \textbf{Privacy of The Person:} reflexive violation
\item
  \textbf{Privacy of Behaviour and Action:} none
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Some psychological diseases
  (e.g.~depression) have physiological impact. Such physiological
  patterns could be detected.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} none
\end{itemiz*iPrivacy of Behaviour and Action}
he Privacy of Behaviour and Action is concerned with one' and social activities (religious, po...l, sexual, \ldots). Ifhis type is violated, following implicit violations are possible:
item
  \textbf{Privacy of The Person:} Religious practices emph include body
  modifications (e.g.~circumcision).
\item
  \textbf{Privacy of Behaviour and Action:} reflexive violation
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Social activities in
  general depend on a certain intellectual attitude. Such an actvity is
  the expressions of such an attitude.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} Recording religious, politcal or
  sexual activities can reveal association with churches, political
  parties or sexual partners.
\end{itemize}

@@

The \textbf{Privacy of The Person} is generally concerned with one could
best understand as \emph{Biometric Privacy}. Friedewald et al. paraphase
it as \emph{``[...] the right to keep body functions and body
characteristics [...] private''}. \textbf{Accelerometer},
\textbf{Rotation Vector} and \textbf{Gyroscope} measure the physical
movement of the mobile device on all three axes. If the moblile device
is carried \emph{``normally''} its safe to say that those sensors also
measure the movments of its carrier. So his privacy is infringed
regarding biometric behaviour, as it is captured automatically.
(\textbf{Note:} This is not to be confused with the \textbf{Privacy of
Behaviour and Action} which is used for the social aspects of behaviour
action, e.g.~praying, sexual habits or poltical activities.)

@@

The \textbf{Privacy of Association} sates that everyone has the
\emph{``right to associate with whomever they whish, without being
monitored [automatically without reasonable suspicion]''}. This
includes indivisuals and organizations. \textbf{WLAN} and
\textbf{Bluetooth} sensors provide the ability to monitor such
associations if their lists contain kown entities. If one frequently
connects with an organizational wirelss network, e.g.~an university
network, an association can be deduced (student or staff). The same goes
for the \textbf{Bluetooth} sensor, if it is stationary. Additionally, if
the recorded bluetooth clients are mobile, it is more or less possible
to deduce association with the technical identity of (yet) anonymous
individuals.

@@

\subparagraph{1 Privacy of the Person private''} \cite{1}. Here we are
concerned wi the personal physiological and psychological p and  This privacy is threat...f \textbf{body characteristics}weight, height,, dna,\ldots) or
depression emph therapists or other doctors) \textbf{can beevealed orii and emph+Gov project collects sensor data from mobile devices
(accellerometer, location, \ldots). By a...g \emph{human activityecognition (emph)} techniques we could detect certain movement patterns
we know the position with of indiviual citizens with a sufficientccurancy, and the Live+Gov project is only applied to a destinct urban
area. So we could link HAR data with the yellow pages, filter for
medical specialists and limit the possibilities of pathologic
conditions. But even without HAR data we could determine a likelihood
for certain conplaints. Frequent vistits to the dentist does not imply
healthy teeth.

@@

\emph{``This type is also concerned with the `protection against
disclosure of personal matters' through behaviour''}
\cite{1}. This type is concered with religous
practices, sexaul habits, political activities, etc. revealed through
observation. For the Live+Gove project this type is related to t is recirded by default and by linking it to maps a and li phone books those *``personal matters*" could be
disclosed by frequently visited places (c...s, brothels, party headuaters, \emph).

communications' either
electronic or face-to-face''} \cite{1}. This type
is threatened if we intrude the secrecy of correspondence, posts and
telecommunications, personal direct communication or right to free
discussion without third parties listening. The Live+Giv project only
could threaten this type by using mobile client application as trojan
horse, collecting any communication data (chat, sms, microphone).

@@

\emph{``This type is concerned with `making sure that individuals's data
is not automatically available to other individuals and
organisations'\,''} \cite{1}. This is
Informational Privacy in an intuitive sense regarding data like:

@@

\emph{``This type is the right `not to share their thoughts or feelings
or to have those thoughts or feeling (sic!) revealed'\,''}
\cite{1}. This means thoughts and emotions must
not be detected autmatically. Intuitively the Live+Gov system seems
unable to threaten this type. However, considering the issue component
of the Urban Maintaince use case, this might reveal information about
one's thoughts regarding the community in a positive manner. Solely by
taking part we could assume a caring personality. This threatens one's
privacy in a rather technical sense, but does not necessarily impose any
harm.

@@

\emph{``This type is the right `to move about in public or semi-public
space withoug being identified, tracked or monitored'. Additionally this
type is concerned with the protection of one's home and private places
(`right to solitude')''} \cite{1}. The location
dimension of this type is relatively easy to understand: The
geo-position of citizens cannot be monitored by default. However, by
actively taking part in the Live+Gov project, the locational privacy of
citizens is threatened by default because data of the location sensor
will be collected. The space dimension is more complex, but can be
simplified with a \emph{``right to solitude''}. This dimension could be
threatend with the invasion of personal space in any means, i.e.~by
disrespecting one's right to an inviolate home or by undercutting one's
comfort zone in an conversation. Live+Gov only utilizes the mobile
devices of citizens, so we could disrespect the former by activating the
phone's micropone and start recording.

@@

\emph{``This type is the right `to associate with whomever [one]
wish, withoug being monitored'.''} \cite{1}. This
means that one's associations must not be recoreded by default
independet from any suspicion. Anyhow, it does not mean that this right
cannot be forfeit given a reasonable suspicion. The Live+Gov project
could easily threaten this type just by linking locational data with
yellow pages and a map. Even if an association graph cannot be deducted
for individual citizens, we could aggregate the data to create an
association graph for a whole population as the Live+Gov system is
applied to a restricted urban area.

@@

This is a note on an excerpt from the article \emph{Sociotechnical
Architecture for Online Privacy} \cite{1} called
\textbf{The 7 C's of user privacy control}. Those 7 C's are aspects
which should be covered by measures for implementing user privacy. They
derive from an interpretation of privacy which could be summarized as
\emph{``One's ability to control/seclude information about themselve''}.
